% 02_Summary
%
With unmanned vehicles, there are always on-board and off-board components. Data transmission between those components is of vital importance. Depending on the distance between vehicle and ground station, different data transmission technologies are ideal. \\
In a previous project, the hardware for a Serial Switch has been designed that features four RS-232 interfaces to connect data processing and generating devices and four RS-232 interfaces to connect modems for data transmission. The application running on the designed base board assembles data packages with the received data from its devices and sends those data packages out to the modems for transmission. The corresponding second Serial Switch receives those data packages, checks them for validity and extracts the payload to send it out to its devices.\\
A Teensy 3.5 development board acts as the main micro controller and is running with FreeRTOS. Baud rates of the serial interfaces, acknowledges, package resend behavior and other parameters can be configured by altering the config file located on the SD card.\\
The main goal of this project is to add data security and to improve transmission reliability. The software developed in the previous project is taken as a basis, but it needed further work before any new features could be implemented. \\
First, logging, CRC check and other items needed were added. Then, the runtime behavior of the application was analyzed with the Percepio Tracelyzer to ensure sufficient CPU resources left for encryption.\\
Then, data reliability was improved in the following ways:\begin{itemize}
    \item Adding an error correction code to recover original data from faulty packages
    \item Enhancing the resend behavior and supporting transmission of the same package over multiple wireless interfaces
    \item Adding a Smart Wireless Selection algorithm that choses the most reliable wireless channel for package transmission
\end{itemize}
The Golay error correction code was chosen to recover data lost due to interference. The retransmission behavior was enhanced to supports sending the same data over multiple wireless connections and the software was prepared to soon support payload reordering in case the packages get jumbled. A Smart Wireless Selection algorithm was developed that choses the most reliable wireless connection depending on package loss ratio per wireless link and a cost value configurable in the config file.\\
Data security was introduced by adding a crypto acceleration unit to the software project that can later be used to encrypt the communication between two Serial Switches. Suggestions about encryption key storage are given within this document. Integrity of the log files can be guaranteed by adding a hash value to the logged data. The application should thereby not only feed the hashing algorithm with the logged data but also with a secret random number to ensure tempering with the log file is detected. The unique ID of the Teensy 3.5 is suggested to be used as this secret random number.